Hierarchical Reverberation Mapping

### 2013-10-29 Paper/ms.tex
Conclusions etc

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from 100 AGN. The data for each object was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is scaled to half that of the line data, and the
measurement noise is 0.25, or 1\%, on the line data. See Figure~\ref{fig:data}
for three illustrative data sets from the sample.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/data.eps}
\caption{Three simulated data sets, out of a total of 100.\label{fig:data}}
\end{center}
\end{figure}

We computed the stacked cross-correlation function for the 100 data sets.
The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated by looping over pairs of points
(one selected from the continuum data set, and another from the line data set),
and accumulating mass when the lag between the two points is between $\tau$
and $\tau + \delta$.
\begin{eqnarray}
X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
\end{eqnarray}
The denominator is the number of pairs of points that fall within the lag range
being considered, $[\tau, \tau + \delta]$, denoted $n_{\rm pair}$ by
\citet{2012MNRAS.427.2701F}.
The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
from our 100 simulated AGN data sets. There is a clear peak around 10 days.

@@

As the data does not contain measurements at all possible time lags, the stacked
CCF will always require some smoothing. Here, the smoothing is supplied by the
choice of a bin width $\delta$. The stacked CCF has a substantial width. One
weakness of the stacked CCF method is that it is not clear whether this width
is caused by real diversity in the sample of AGN, or whether it is simply caused
by the difficulty in measuring the lag $\bar{\tau}$ of an object with such
sparse data. By contrast, the hierarchical Bayesian approach clearly separates
these two concepts. The diversity of the population is quantified by $\sigma$,
whereas uncertainty about the central value $\mu$ is described by the
posterior distribution for $\mu$.

@@

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. The joint posterior distribution for $\mu$ and
$\sigma$ is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
was uniform inside the rectangle shown, and the posterior distribution covers
a much smaller area, indicating that the data contained a lot of information
about the hyperparameters.

@@

The marginal distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$.

@@

\section{Conclusions}\label{sec:conclusions}
Reverberation mapping is an important, yet observationally intensive, technique in studies of active galaxies.

>>>>

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from 100 AGN. The data for each object was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is scaled to half that of the line data, and the
measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
for three illustrative data sets from the sample.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/data.eps}
\caption{Three simulated data sets, out of a total of 100. It is difficult to
infer the lag $\bar{\tau}$ for any of these objects (although there is some
information available). See Figure~\ref{fig:example_posteriors} for the
$\bar{\tau}$ posterior distributions for these three data sets.
\label{fig:data}}
\end{center}
\end{figure}

We computed the stacked cross-correlation function for the 100 data sets.
The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated by looping over pairs of points
(one selected from the continuum data set, and another from the line data set),
and accumulating mass when the lag between the two points is between $\tau$
and $\tau + \delta$.
\begin{eqnarray}
X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
\end{eqnarray}
The denominator is the number of pairs of points that fall within the lag range
being considered, $[\tau, \tau + \delta]$, denoted $n_{\rm pair}$ by
\citet{2012MNRAS.427.2701F}.
The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
(on a log scale) from our 100 simulated AGN data sets.
There is a clear peak around 10 days, and the full width at half maximum,
while not strictly well defined, is roughly 0.25 dex.

@@

As the data does not contain measurements at all possible time lags, the stacked
CCF will always require some smoothing. Here, the smoothing is supplied by the
choice of a bin width $\delta$. The stacked CCF has a substantial width. One
weakness of the stacked CCF method is that it is not clear whether this width
is caused by real diversity in the sample of AGN, or whether it is simply caused
by the difficulty in measuring the lag $\bar{\tau}$ of an object with such
sparse data. By contrast, the hierarchical Bayesian approach clearly separates
these two concepts.

@@

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
our assumption for the prior on $\bar{\tau}$ given
the hyperparameters is a lognormal distribution with median $\mu$ and
width (standard deviation of $\log(\bar{\tau})$) $\sigma$:
\begin{eqnarray}
\log(\bar{\tau}) \sim \mathcal{N}(\log(\mu), \sigma^2)
\end{eqnarray}

The joint posterior distribution for $\mu$ and
$\sigma$, given the data from $N=100$ AGN,
is shown in Figure~\ref{fig:posterior}. The prior for $\mu$ and $\sigma$
was uniform inside the rectangle shown, and the posterior distribution covers
a much smaller area, indicating that the data contained a lot of information
about the hyperparameters. The true values used to generate the simulated data
are denoted by the star symbol in Figure~\ref{fig:posterior},
and is typical of the posterior distribution, as it should be.

@@

The marginal posterior distribution for $\mu$ is shown in Figure~\ref{fig:posterior2}
along with the posterior predictive distribution for the ``next'' $\bar{\tau}$ value. The inference about $\mu$ can be summarised as
$\mu = 0.892 \pm 0.033$, and the prediction about $\log_{10}(\bar{\tau})$
may be summarised as $\log_{10}(\bar{\tau}) = 0.892 \pm 0.160$. The Bayesian
approach has clearly separated the uncertainty about $\mu$ from the diversity of the
sample, described by $\sigma$.

@@

\section{Conclusions}\label{sec:conclusions}
Reverberation mapping is an important, yet observationally intensive,
technique in studies of active galaxies. This has motivated substantial
research into RM data analysis techniques, as well as less costly observing
strategies. The recent approach of \citet{2012MNRAS.427.2701F} demonstrated
that it is possible to combine information from many sparsely-measured AGN
and infer properties of the sample rather than insisting on accurate results
about a particular object.

In this letter we extended the approach of \citet{2012MNRAS.427.2701F} by
implementing a Bayesian hierarchical model for the data analysis. The main
advantage of this approach is a clear interpretation of the output, which is
a posterior distribution for hyperparameters describing the sample of AGN.

We demonstrated this approach on a simulated data set consisting of 100 AGN
with well-measured continuum light curves but sparsely measured (two epochs per
AGN) broad line light curves. For the simulated data set we were able to obtain
an inference on $\mu$, a hyperparameter describing the typical value of the lag,
to within 0.033 dex (1-$\sigma$ uncertainty), whereas the stacked cross-correlation
function had a FWHM of $\sim$ 0.25 dex. This is possible because a subset of
the objects in the sample will have a measureable lag. We hope this approach
will facilitate informative studies of samples of AGN.
